Untitled

### 2014-12-03 Misc/TrialFile.Rmd

``` {r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}

# Country code
rm(CleanGEM)
dfs <- ls()[1:max(grep(pattern = 'Clean[0-1]*', x = ls()))]

@@

# Country code
# Subset

     CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
                              rownames(Clean10)),
                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
                                    Clean07, Clean08, Clean09, Clean10)))

# Change merged data from wide to long
LongGEM<- melt(data = CleanMerge,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Rename columns
names(CleanMerge) <- gsub("variable", "Year", names(CleanMerge))
names(CleanMerge) <- gsub("value", "Support", names(CleanMerge))

# Create a vector with OECD countries
myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'South Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')

# Subset LongGEM with the countries we need  (Why does 2001 and 2010 data disappear?)
subset_data <- subset(CleanMerge, Country %in% myvars)

# Delete unnecessary column
subset_data$row.names <- NULL

# Arrange subset_data by country and year
GData <- arrange(subset_data, Country, Year)

GData <- GData[order("Country",)]

########### STUCK #############

FinalData <- merge(FinalGEM, GrandData,
                   union("Country", "Year"))
```

>>>>

``` {r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(foreign)
library(countrycode)

# Set working directory
setwd('~/Assign2Education/GEMData')

# Import GEM NES 2001-2010 Data
GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)

## Clean Annual GEM NES Datasets

# Draw out Country and D01 only
Clean01 <- GEM2001[,c("country", "ki01d01")]
Clean02 <- GEM2002[,c("country", "ki02d01")]
Clean03 <- GEM2003[,c("country", "ki03d01")]
Clean04 <- GEM2004[,c("ki04ctry", "ki04d01")]
Clean05 <- GEM2005[,c("KI05ctry", "KI05D01")]
Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]

# Remove unnecessary dataframes from environment
remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)

# Edit column names for each dataframe
Clean01 <- plyr::rename(x = Clean01, 
                                      replace = c("ki01d01" = "2001",
                                                  "country" = "Country"))

Clean02 <- plyr::rename(x = Clean02, 
                                      replace = c("ki02d01" = "2002",
                                                  "country" = "Country"))

Clean03 <- plyr::rename(x = Clean03, 
                                      replace = c("ki03d01" = "2003",
                                                  "country" = "Country"))

Clean04 <- plyr::rename(x = Clean04, 
                                      replace = c("ki04d01" = "2004",
                                                  "ki04ctry" = "Country"))

Clean05 <- plyr::rename(x = Clean05, 
                                      replace = c("KI05D01" = "2005",
                                                  "KI05ctry" = "Country"))

Clean06 <- plyr::rename(x = Clean06, 
                                      replace = c("KI06D01_mean" = "2006",
                                                  "KI06CTRY" = "Country"))

Clean07 <- plyr::rename(x = Clean07, 
                                      replace = c("ki07d01_" = "2007",
                                                  "ki07ctry" = "Country"))

Clean08 <- plyr::rename(x = Clean08, 
                                      replace = c("NES08_D01_MEAN" = "2008",
                                                  "NES08COUNTRY" = "Country"))

Clean09 <- plyr::rename(x = Clean09, 
                                      replace = c("NES09_D01_MEAN" = "2009",
                                                  "NES09COUNTRY" = "Country"))

Clean10 <- plyr::rename(x = Clean10, 
                                      replace = c("NES10_D01_MEAN" = "2010",
                                                  "NES10CRNAME" = "Country"))

# Clean Dataframes
dfs <- ls()[1:max(grep(pattern = 'Clean[0-1]*', x = ls()))]

@@

## Add country codes and place new column at beginning of the data frame

# Create a vector of country codes
W1 <- countrycode(cleaned$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
cleaned$new.col <- W1

# Change the order of columns so country code is first
W2 <- cleaned[,c(4,1:3)]

# Change the name of new.col
names(W2) <- gsub("new.col", "iso2c", names(W2))

## Subset W2 to OECD countries

# Create matrix of OECD countries by iso2c code
myvars <- c('MX','CA','US','FR','AU','AT','BE','CL','CZ','DK','EE','FI','DE','HU', 'IS','IE','IL',
            'IT','JP','KR','LU', 'NL','NZ','NO','PL','PT','SK','SI', 'ES','SE','CH','TR','GB','US','GR')

# Subset W2 with myvars
subW2 <- subset(W2, iso2c %in% myvars)

# Delete unnecessary column
subW2$row.names <- NULL

### 2014-12-03 Presentation/EdEntrePres.Rmd

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

# Duplicate D4 df
Dropped4 <- D4

@@

Table <- gvisTable(Dropped4, 
               options=list(width=230, height=300))

MT <- gvisMerge(Opp_map, Table, horizontal = TRUE)

print(Opp_map, tag = 'chart')

@@

## Distribution of Perception Differences
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(ggvis)

line_plot <- gvisLineChart(Opp1)
print(line_plot, tag = 'chart')

@@

@@

## WayofTeaching
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, cache = FALSE, na.strings = "-")

@@

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

# Duplicate D4 df
Dropped4 <- D4

Table <- gvisTable(Dropped4, 
               options=list(width=230, height=300))

MT <- gvisMerge(Opp_map, Table, horizontal = TRUE)

print(Opp_map, tag = 'chart')

>>>>

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}

# Plot perceived opportunties map
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

# Duplicate D4 (perceived opportunities) df
Dropped4 <- D4

@@

# Print the table
print(Opp_map, tag = 'chart')

@@

## Distribution of Perception Differences
```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")

# Create country vector to subset
myvars2 <- c('US','FR','DE','JP','GB')

# Subset Opp2
Opp2 <- subset(Opp1, iso2c %in% myvars2)

# Melt Opp2 df
Opp3 <- melt(data = Opp2,
                  id.vars = c("Country", "iso2c"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Edit column names
names(Opp3) <- gsub("value", "WayofTeaching", names(Opp3))
names(Opp3) <- gsub("variable", "Year", names(Opp3))

Opp3$iso2c <- NULL

# Create plot
ggplot(Opp3,aes(x=Year,y=WayofTeaching,colour=Country,group=Country)) + geom_line()

@@

subset
ggplot1
geom_line color each country
colors by country 4-5

@@

## WayofTeaching
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")

@@

# Change data from long to wide format
WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")

# Delete variable name in Year columns
names(WT) <- gsub("WayofTeaching.", "", names(WT))

# Generate a new column with mean of all other columns
WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010")), na.rm = TRUE)

# Drop year columns, leaving only mean column
WT$'2001' <- NULL
WT$'2002' <- NULL
WT$'2003' <- NULL
WT$'2004' <- NULL
WT$'2005' <- NULL
WT$'2006' <- NULL
WT$'2007' <- NULL
WT$'2008' <- NULL
WT$'2009' <- NULL
WT$'2010' <- NULL
WT$'2011' <- NULL
WT$'2012' <- NULL
WT$'2013' <- NULL
WT$row.names <- NULL

# Create 
WT[, 3] <- round(log(WT[, 3]), digits = 2)
```

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
library(googleVis)

# Plot
WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

Table2 <- gvisTable(WT, 
               options=list(width=230, height=300))

WTT <- gvisMerge(WT_map, Table, horizontal = TRUE)

print(WT_map, tag = 'chart')

### 2014-12-03 Presentation/PresMisc/MiscPresStuff.Rmd

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

# Interactive histgram (isn't interactive in knitted docs)
D4 %>% 
  ggvis(~mean, fill := "#2c7fb8") %>% 
  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
                   center = input_slider(0, 2, step = 0.05, label = "center"))

@@

>>>>

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggvis")
# Interactive histgram (isn't interactive in knitted docs)
D4 %>% 
  ggvis(~mean, fill := "#2c7fb8") %>% 
  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
                   center = input_slider(0, 2, step = 0.05, label = "center"))

@@

##################

###################################################

library(googleVis)
library(reshape2)

# Melt Opp1 (Perceived opportunities 2001:2013 OECD)
dfChart1 <- melt(data = Opp2,
                  id.vars = c("Country", "iso2c"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Change column name of value and variable
names(dfChart1) <- gsub("value", "WayofTeaching", names(dfChart1))
names(dfChart1) <- gsub("variable", "Year", names(dfChart1))

library(rCharts)

# rChart
Try1 <- transform(dfChart1, Year = as.character('Year'))

sub_aust <- subset(Try1, Country == "Australia")

m1 <- mPlot(y = "WayofTeaching", x = "Year", type = "Line", data = Opp3)

m1$set(pointSize = 0, lineWidth = 1)

m1$print('chartTest')
```
